\chapter{Information Gathering}

\noindent 
\paragraph{\Large Introduction }\textbf{}\\~~We know about that people in our country, who want to buy a new car, must have to go first in the car showroom., then choose his/her cars, then purchase it. This process is very time consuming. So, our main goal is to reduce the time-consuming factors. For making our project successful, we need to follow some steps gradually for the entire development of this project. Regarding this, information gathering is the first and foremost step. \\


\noindent 

\noindent 
\section{ Objectives of Information Gathering  \&  \newline Interview}

\noindent The name of our project is CAR Rent \& Sell. To make the project user-friendly, by useful data and information, it is important to interview authority of the car showroom. The information obtained from the relevant people working there would help us for the project to be perfect and precise work. Here we have constructed interview questions to gather information requirements and structured them in a meaningful way. All this information is gathered from the authority who invoked us to work for this project. According to the gathered information and collection of data, we have numerous scopes to improve the features and add new functionalities in future.


\noindent 

\noindent 

\noindent 
\section{ Questionnaire \& Interview Pattern}

\noindent Interviewing is a specific form of meeting or conference, and is usually limited to two persons, the interviewer and the interviewee. We have assembled information using the following 1 methods:

\begin{enumerate}
\item  \textbf{Interview of the authority :}We interviewed Mr. Tanvir Ahmed Iftekhar who is the Sales Executive of the Navana Limited.

\end{enumerate}

\noindent For both methods of question and answers, we have chosen \textbf{Diamond shaped Structure}. The diamond-shaped structure for interviewing combines the pyramid and funnel structure. This structure entails beginning in a very specific way, then examining general issues, and finally coming to a very specific conclusion. So, we decided to work with this structure.  

\noindent In the interview process, we have included:

\begin{enumerate}
\item  4 Close Ended questions at first. 

\item  4 Open Ended questions in the middle

\item  2 Close Ended questions at last
\end{enumerate}
\noindent The table pattern for interview \& questionnaire is given below:

\begin{table}



\begin{tabular}{|p{1.3in}|p{1in}|p{1.1in}|p{1.1in}|} \hline 
\multicolumn{4}{|p{5in}|}{\textbf{~~~~~~~~
~~~~~~~~~Car Rent and Sell Website}} \\ \hline 
\textbf{Authors:\newline \newline }Md.~Rubel~Mia\newline Asadullahhil~Galib\newline Narayan~Das~Nitol\textbf{} & \textbf{Date:\newline \newline }23-05-2018 & \textbf{Time:\newline \newline }02:30 pm \textbf{} & \textbf{Duration:\newline \newline }\newline 60mins \textbf{} \\ \hline 
\multicolumn{2}{|p{2in}|}{\textbf{Participants:\newline  }Mr. Tanvir Ahmed Iftekhar\textbf{\newline }Sales Executive – Navana Limited \newline } & \multicolumn{2}{|p{2.4in}|}{\textbf{Comments:\newline }\newline We have got a clear idea of the website that authority requires and the current existing systems \newline } \\ \hline 
\end{tabular}

\caption{ Interview  Questionnaire Pattern of Car Rent \& Sell Website}

\end{table}

\noindent 
\section{ Reason To Select Interview Personnel}

\noindent As Mr. Tanvir Ahmed Iftekhar is the Sales Executive of Navana Limited, he has the utmost knowledge of which is required for his company to flourish further. He knows better about entire sector of this company. That’s why we have selected for the interview.

\noindent \\


\noindent 

\newpage 

\subsection{ Interview Questions \& Answers }
\begin{enumerate}
    \item \textbf{How many people are working in this showroom?}
    \noindent \textbf{\underbar{Answer:}}65.
    
    \item \textbf{How many people are working in this showroom?}\newline
    \noindent \textbf{\underbar{Answer:}}Around 500.
    
     \item \textbf{Do you have any existing website for your company?}\newline
    \noindent \textbf{\underbar{Answer:}}Yes. It is www.amartoyota.com.
    
    \item \textbf{Do you want any online customer support?}\newline
    \noindent \textbf{\underbar{Answer:}}Yes. 
    
    \item \textbf{How many cars you are selling in a month?}\newline
    \noindent \textbf{\underbar{Answer:}}Well, its very tough to say. Because it is not constant. It varies from month to month. As an example, sometimes we sell around 5 cars in a month. And sometimes we sell around 100 cars in a month. In the month of May-July, we sell maximum cars as it is the month of Government Purchase. Government alone buys maximum car for their employee and higher authority.

    
    \item \textbf{How many categories you want to include in this website?}\newline
    \noindent \textbf{\underbar{Answer:}} There should be 5 categories in the website :\newline
	\begin{enumerate}
		\item Choice
		\item Test Drive
		\item Verification
		\item Rent a Car
		\item Services
	\end{enumerate}
    
   
    \item \textbf{Do you want to include any virtual reality system in this website?}\newline
    \noindent \textbf{\underbar{Answer:}} Obviously. I want a 3D view of our showroom where people can see like the real one. Our customer can get the real feel of our showroom seating at their house. Customers can open the door of a car virtually, can see the windshield virtually, also can drive the card virtually. This will help our customers to select their cars.
    
    \item \textbf{How you will control the Car Rental System of this website?}\newline
    \noindent \textbf{\underbar{Answer:}}Those cars which we want to rent, there will be a GPS system included with every cars. We can track any cars as we want. So, our cars will remain safe. We will provide 2 packages for our clients for rental purpose :
	\begin{enumerate}
		\item Car with Driver
		\item Car without Driver		
	\end{enumerate}
	\noindent Car with a driver - in this package, our official driver will drive the cars \newline
	Car without driver - in this package, our clients will drive the cars.

    
    \item \textbf{Which things is the must you want to include in the website?}\newline
    \noindent \textbf{\underbar{Answer:}}A realistic picture of the car with the price tag.  
    
    \item \textbf{Do you want any online review system for every car in your showroom?}\newline
    \noindent \textbf{\underbar{Answer:}}Yes. We will upload every video of every single cars of your showroom so that our customer will get a clear idea.
    
    \end{enumerate}

\section{Revised Requirement Analysis}

\noindent Through all the information collection, we revised our work and concluded that along with our features. For this constant update of information, we will need to create an Virtual Reality System. This will remain in our future goal for this application.

\begin{enumerate}
\item  User friendly interface.

\item  Well-interactive interface between customer and employee.

\item  Adding a searchbox for initial search.

\item  Admin panel is a must for handling the dealer, product and employee.

\end{enumerate}

\noindent 

\noindent 
\section{ The list of Activities}

\noindent We have interviewed people of a company before designing the project. We have collected the following information:

\begin{enumerate}
\item  How the services are provided to the customers.

\item  How the services are provided to the customers.

\item  How they will manage the entire system.

\item  The security management of the rental cars.

\item  Virtual Reality of the showroom.

\end{enumerate}

\noindent 
\noindent
We also wanted to know the problems they are encountering for not having any dynamic website. We gathered the critical information from them regarding the types of features they want in the website. All these data and information would help us to design the website.

\noindent 
\noindent

\section{ Conclusion}

\noindent The interview and survey process gave us the opportunity to visit and interview different people and helped us a lot to know what users actually want from a website which contains information of such things related to buy rent a car company. These information and data will help us to design a website according to user choice and make our work easier

\noindent 

\noindent 

\noindent 

\noindent 

