\chapter{Discussion}

\noindent 

\noindent 
\paragraph{\large{Conclusion}}

\noindent\\ The main focus of Car Rent and Sell website is to consume time of customers to choice cars and also to rent a car for their different purpose. Customers do not need any physical contact of the showroom , rather than they can choose car from anywhere of the country. We have initially started our project by our imagination and the requirements of the company. After that we have gone through all the feasibility analysis, cost benefit analysis, cash flow analysis and so on. We have also designed our Gantt chart and started working by following the project scheduling of our project. Then we interviewed the authority. We also gathered information to know the requirements of the authority.

\noindent After the interview we have designed our Data Flow Diagram (DFD) by which we got the specific vision of our project and got a clear graphical representation of our system's requirements. After designing the DFD, we designed our Use Case Diagram.Then we designed the entity relationship diagram (ERD) which is the logical structure of database and shows relationships of entity sets stored in a database. We have also designed our class diagram which contains all relevant relations and data types.


\noindent 

\noindent 
\section{ Limitation}

\noindent We tried our best to impliment all the features of our project which the authority wants. We have collected every important information about this company which is related to our project. But after all, we have some limitations in our project which we could not impliment at all but have plan to do it in future.

\noindent The limitations of our project are given below:

\begin{enumerate}
\item  We have designed our website only for 1 showroom.

\item  Rental management system is not satisfactory.

\item  Vistual Reality System is not implimented.

\item  Online paylemt is not included in our website.

\item  Online Customer Support feature is not working.
\end{enumerate}

\noindent 

\noindent 
\section{ Future Work}

\noindent In future we will fulfill the limitations of our website which we mentioned before. Then we have also some idea related to Car Rental System which will give customer more pleasure and satisfaction. The authory also wants some unique features for their Car selling and Rental system by which their customer will get 100% satisfaction.

\noindent The future work of our project is given below:

\begin{enumerate}
\item  Automatic Car rental management system

\item  Online Car rental system like UBER where user can select the destination point of their travel.

\item  We will implement Virtual Reality System by which the customer get the real feel of the car showroom. They can touch the cars virtually . Also see all the specifications of the car as like real.

\item  Online payment system with MasterCard/Visa/CreditCard/Bkash.

\item  24/7 online customer support.

\item  Well-interactive interface between customer and company.

\end{enumerate}